### 2021-10-28 theoriezf/Article.tex
misc

\begin{document}

\section{Introduction}

@@

@@

>>>>

%\usepackage{paralist, tabularx}
\usepackage{oldlfont,amssymb,epsf,stmaryrd,epsfig,color}\usepackage{amsmath}
%\usepackage{hyperref}
%\usepackage{framed,multicol,changepage}
%\usepackage{graphicx}
\usepackage[dvipsnames]{xcolor}
%\usepackage{skull,ifoddpage,marginnote}
%\usepackage{pifont}
%\usepackage{graphicx}
%\usepackage{ebproof}
%\usepackage{mathtools}
%\usepackage{bm}
%\usepackage{stmaryrd}
%\usepackage{cleveref}
%\usepackage{tikz}
%\usepackage{import} % For inkscape generated files

\input{macros.tex}

\begin{document}
\thispagestyle{empty}
\section{Introduction}

@@

\subsection{Sorts}

The langage of the theory IZmod uses four sorts. The first two are for
the pointed graphs and for the nodes of the pointed graphs.  In
\dedukti, we thus introduce two constants $\Graph$ and $\Node$ of type
$\Type$
\begin{verbatim}
constant symbol Graph : TYPE;
constant symbol Node : TYPE;
\end{verbatim}
As we have two sorts, we would need two universal quantifiers and two
existential quantifiers, one for each sort.  We rather use another
solution \cite{theoryU} that is to declare a constant $\Set$ of type
$\Type$ for codes of sorts, a function $\El$ of type $\Set \ra \Type$,
two constants $g$ and $n$ of sort $\Set$ and rewrite rules
$$\El~g \lra \Graph$$
$$\El~n \lra \Node$$

The two other sorts of the theory IZmod are for classes of nodes and
for binary relations on nodes.  In \dedukti, the sort of classes is
just $\Node \ra \Prop$ and that of binary relations
$\Node \ra \Node \ra \Prop$. To quantify on such sorts, we introduce
constants $\omicron$ of type $\Set$ and $\arr $ of type
$\Set \ra \Set \ra \Set$ and rewrite rules
$$\El~\omicron \lra \Prop$$
$$\El~(x~\arr~y) \lra (\El~x) \ra (\El~y)$$
Note that $\El~(n~\arr~\omicron)$ reduces to $\Node \ra \Prop$ and 
$\El~(n~\arr~(n~\arr~\omicron))$ reduces to $\Node \ra \Node \ra \Prop$.

The symbols $\Graph$, $\Node$, $g$ and $n$ are specific to the
expression of $IZmod$ in \dedukti. In contrast the symbols $\Set$,
$\El$, $\omicron$, and $\arr$ are part of the standard library of 
\dedukti.

\subsection{Signature}

The signature of $IZmod$ contains 31 symbols. As we have replaced the
sorts for classes and relations with the \dedukti types
$\Node \ra \Prop$ and $\Node \ra \Node \ra \Prop$, we do not need
specific predicate symbols to apply a class to a node or a relations
to two. In the same way, we do not need comprehension axioms for 
classes and relations.

In the same way, the equality symbol is part of the standard library of 
\dedukti.

So the signature is reduced to 26 symbols.

$$eta : \Graph \ra \Node \ra \Node \ra \Prop$$
$$root : \Graph \ra \Node$$
$$cr : \Graph \ra \Node \ra \Graph$$
$$o : \Node$$
$$O : \Node$$
$$i : \Node \ra \Node$$
$$i' : \Node \ra \Node$$
$$j : \Node \ra \Node$$
$$j' : \Node \ra \Node$$
$$I : \Node \ra \Prop$$
$$J : \Node \ra \Prop$$
$$\rho : \Graph \ra \Node$$
$$\hat{\rho} : \Node \ra \Graph$$
$$Succ : \Node \ra \Node$$
$$Pred : \Node \ra \Node$$
$$Null : \Node \ra \Prop$$
$$Nat : \Node \ra \Prop$$
$$< : \Node \ra \Node \ra \Prop$$
$$simeq : \Graph \ra \Graph \ra \Prop$$
$$\in : \Graph \ra \Graph \ra \Prop$$
$$join : \Graph \ra \Graph$$
$$pair : \Graph \ra \Graph \ra \Graph$$
$$powerset : \Graph \ra \Graph$$
$$comp : \Graph \ra \El valuation \ra \El formula \ra \Graph$$
$$omega : \Graph$$
$$Cl : \Graph \ra \Graph$$

À faire en verbatim plutôt qu'en math mode, mais un pb avec certains
caractères unicode

@@

$$comp : \Graph \ra \El valuation \ra \El formula \ra \Graph$$

In $comp$ we may have noticed the presence of valuation and formula. 
Indeed.

\section{The theory of pointed graphs}
